Dynein walks like an Imperial AT-ST

### 2017-11-15 reorganize/papers/paper/paper.tex
demo wide figure
Add current parameter table to paper.
remove watermark from paper
Add two new papers to notes.tex.
fail more nicely when latex fails

@@

@@

>>>>

% the follow ing causes latex to not wait interactively
\nonstopmode

\setboolean{displaywatermark}{false}

@@

\input{../../data/paper_stepping_parameters.tex}

@@

\subsection*{Results}

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/paper-plot.pdf}
\caption{Placeholder image of a frog with a long example caption to show justification setting.}
\label{fig:trajectory}
\end{figure*}

\begin{figure}%[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/paper-plot.pdf}
\caption{Placeholder image of a frog with a long example caption to show justification setting.}
\label{fig:trajectory}
\end{figure}

\begin{table}%[tbhp]
\centering
\caption{Parameters used in model simulation.}
\begin{tabular}{lrrr}
Parameter & Model & Experimental & Source \\
\midrule
$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
$k_b$ & $\kb s^{-1}$&  & \\
$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
$L_s$ & $\ls nm$ & \cite{nativestructure} & \\
$L_t$ & $\lt nm$ & \cite{nativestructure} & \\
$\theta_b$ & $\eqb$ &  & \\
$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
$\theta_t$ & $\eqt$ &  & \\

\bottomrule
\end{tabular}

%% \addtabletext{nomenclature for the TSs refers to the numbered species in the table.}
\end{table}

\begin{figure}%[tbhp]
\centering
 \begin{minipage}{.3\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-1-cryoem}
   \label{fig:modlengths}
 \end{minipage}%
 \begin{minipage}{.3\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-1-superimposed}
   \label{fig:modlengths}
 \end{minipage}%
 \begin{minipage}{.3\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-1-model}
   \label{fig:explengths}
 \end{minipage}
 %
 \begin{minipage}{.3\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-2-cryoem}
   \label{fig:modlengths}
 \end{minipage}%
 \begin{minipage}{.3\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-2-superimposed}
   \label{fig:modlengths}
 \end{minipage}%
 \begin{minipage}{.3\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-2-model}
   \label{fig:explengths}
 \end{minipage}
\caption{\textbf{Model schematic superimposed on cryo-EM images of native dynein.} Native cryo-EM images of the full dimerized dynein complex composed of light, intermediate and heavy chains, from \cite{nativestructure}. Model schematics are superimposed for illustrative purpose; shown angles to not represent expected \textit{in vivo} equilibria. Schematics are shown docked to a microtubule for illustrative purposes.}
\label{fig:modelparams}
\end{figure}

\begin{figure}%[tbhp]
\centering
 \begin{minipage}{0.5\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-prestroke}
   \label{fig:prestrokeangle}
 \end{minipage}%
 \begin{minipage}{0.5\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-poststroke}
   \label{fig:poststrokeangle}
 \end{minipage}
 %
 \begin{minipage}{\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-binding-angle}
   \label{fig:bindingangle}
 \end{minipage}
 \begin{minipage}{\textwidth}
   \centering
   \includegraphics[width=\linewidth]{figures/schematic-full}
   \label{fig:allangles}
 \end{minipage}
\caption{\textbf{Schematic of model equilibrium angles over cryo-EM images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke dynein heavy chains superimposed with model motor angles, both from \cite{burgess-paper}. \textbf{c.)} Axonemal dynein bound to MT with model binding angle superimposed, from \cite{leschziner}. \textbf{d.} Full native dynein cryo-EM image bound to an MT with model superimposed, from \textbf{nativestructure}.}
\label{fig:modelangles}
\end{figure}
